method

### 2022-06-07 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex

\emph{Part three: ER choice.} After the discounting part, participants will choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
Importantly, there will be no further instruction on what basis they should make their decision.
Participants should make their decision freely, according to criteria they consider important for themselves.
However, participants will be asked to state the reasons for the decision afterwards.
As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.

>>>>

\emph{Part three: ER choice.} After the discounting part, participants will choose which one of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
Importantly, there will be no further instruction on what basis they should make their decision.
Participants should make their decision freely, according to criteria they consider important for themselves.
However, participants will be asked to state the reasons for the decision afterwards.
As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.

### 2022-06-07 06_Paper/ER-ED/method.Rmd

*Part three: ER choice.* <br> After the discounting part, participants will choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
Importantly, there will be no further instruction on what basis they should make their decision.
Participants should make their decision freely, according to criteria they consider important for themselves.
However, participants will be asked to state the reasons for the decision afterwards.
As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.

>>>>

*Part three: ER choice.* <br> After the discounting part, participants will choose which one of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
Importantly, there will be no further instruction on what basis they should make their decision.
Participants should make their decision freely, according to criteria they consider important for themselves.
However, participants will be asked to state the reasons for the decision afterwards.
As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.
